The Dynamics of Normalization Reweighting (target journal: Neuron)

### 2022-05-24 manuscript.Rmd
Update manuscript.Rmd

@@

samplerate <- 1000
targetF <- 5
maskF <- 7
    binwidth <- 1000
    tindex <- 1 + targetF*(binwidth/samplerate)
    mindex <- 1 + maskF*(binwidth/samplerate)

@@

>>>>

hdata <- read.csv('~/Google Drive/Current work/R scripts/EEG analysis/headerfile.csv', header = TRUE)

@@

samplerate <- 1000
targetF <- 5
maskF <- 7
duration <- 6
    binwidth <- 1000
    tindex <- 1 + targetF*(binwidth/samplerate)
    mindex <- 1 + maskF*(binwidth/samplerate)
    legaltriggers <- c(210,211,220,221,230,231,240,241)

@@

osfproject <- osf_retrieve_node("ab3yv")
componentlist <- osf_ls_nodes(osfproject)
EEGID <- pmatch('Raw EEG data 1',as.character(unlist(componentlist[,1])))
EEGID[2] <- pmatch('Raw EEG data 2',as.character(unlist(componentlist[,1])))

subjcounter <- 0
for (datahalf in 1:length(EEGID)){
  EEGtoken <- componentlist[EEGID[datahalf],2]
  EEGfiles <- osf_ls_files(EEGtoken,n_max=300)
  for (f in 1:nrow(EEGfiles)){
    subjcounter <- subcounter + 1

    # first check if we have this participant's data
    if (!file.exists(paste0('temp/EEGprocessed/S',subjcounter,'data.RData'))){
      # if we haven't processed the data, check if we need to download the raw data
      if (!dir.exists(paste0('temp/raw/S',subjcounter))){
        if (!file.exists(paste0('temp/raw/S',subjcounter,'.zip'))){
          osf_download(EEGfiles[f,], path='temp/raw/',progress=TRUE)
        }
          unzip(paste0('temp/raw/S',subjcounter,'.zip'),exdir='temp/raw/')
          file.remove(paste0('temp/raw/S',subjcounter,'.zip'))
      }
    # if necessary, process the data for this participant

      d <- dir(paste0('temp/raw/S',subjcounter), pattern='*.csv.gz',full.names=TRUE)
      condcounter <- (1:4) * 0
      alltrials <- array(0,dim=c(50,4,9000,64))
      subjwaves <- array(0,dim=c(4,9000,64))
      trialsincluded <- matrix(0,nrow=4,ncol=64)

      for (block in 1:length(d)){
      EEGdata <- read.csv(d[block], header = TRUE)
      electrodes <- colnames(EEGdata)

     triggertimes <- (1:64) * 0
    counter <- 0
    for (n in 1:nrow(EEGdata)) {
      if (EEGdata$Trigger[n] %in% legaltriggers) {
        counter <- counter + 1
        triggertimes[counter] <- n
      }
    }

     for (tr in 1:counter) {
      cond <- which(legaltriggers == EEGdata$Trigger[triggertimes[tr]])
      cond <- ceiling(cond/2)
      condcounter[cond] <- condcounter[cond] + 1

      # # horrible hack to fix one trial for P227
      # if (33-samplerate+(triggertimes[tr])<0){
      #   if (pno == 227){triggertimes[tr] <- triggertimes[tr] + 150}
      #   if (pno == 279){triggertimes[tr] <- triggertimes[tr] + 150}
      #  }
    for (ch in 1:64){     
      alltrials[condcounter[cond],cond,,ch] <- as.matrix(EEGdata[33-(1.5*samplerate)+(triggertimes[tr]:(triggertimes[tr] + samplerate * (3+duration) - 1)), ch+3])}

      for (cond in 1:4){
        for (ch in 1:64){

          temp <- alltrials[1:condcounter[cond],cond,,ch]

          spec5 <- NULL
          spec7 <- NULL
          for (t in 1:condcounter[cond]){
            spec <- fft(temp[t,1501:7500])
            spec5[t] <- spec[6*5+1]
            spec7[t] <- spec[7*5+1]
          }
        spec5[which(is.na(spec5))] <- 0
        spec7[which(is.na(spec7))] <- 0
      if (sum(abs(spec5))>0){  
      tempxy <- data.frame(Re(spec5),Im(spec5))
      D5 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
      tempxy <- data.frame(Re(spec7),Im(spec7))
      D7 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))      
      i <- which(D5<3 & D7<3)
      trialsincluded[cond,ch] <- length(i)
      subjwaves[cond,,ch] <- colMeans(temp[i,])
      }   
        }
      }

      qdatasubj <- read.csv(paste0('temp/raw/S',subjcounter,'/questionnairedata.csv'))
      save(file=paste0('temp/EEGprocessed/S',subjcounter,'data.RData'),list=c('qdatasubj','condcounter','trialsincluded','subjwaves'))
    }
